---
title: How Does the State Speak of Globalisation? A Quantitative Text-Mining Approach
author:
- name: Justin Murphy
  affiliation: University of Southampton
  email: j.murphy@soton.ac.uk
date: April 2014
abstract: Scholars argue that globalisation is strategically deployed by governments [@Hay:2011dh]. This is the first large-N statistical analysis of this argument.
...

```{r setup, include=FALSE, results="hide", warning=FALSE}
opts_chunk$set(fig.width=10, fig.height=7, fig.show='hold', echo=FALSE, message=FALSE, warning=FALSE) 
```


```{r, echo=FALSE, results='hide', message=FALSE}
require(tm)
require(ggplot2)
require(xtable)
require(pander)
setwd("~/Dropbox/gh_projects/uk_govt_web_archives")
load("data/globalisation_dtm.Rdata")
load("data/globalisation_corpus.Rdata")
inspected <- inspect(dtm)  # inspect the dtm
```


### Descriptive Statistics
```{r globalisation_frequency_plot, echo=FALSE, cache=TRUE, fig.cap="Most frequent terms"}
frequencies<-head(sort(colSums(inspected), decreasing=TRUE), n=50) # list terms in order of frequency, with counts
terms<-names(frequencies)
freqs<-data.frame(terms,frequencies)
freqs$terms <- factor(freqs$terms, levels=freqs$terms[order(frequencies)], ordered=TRUE)
options(scipen=999)
ggplot(data=freqs, aes(x=terms, y=frequencies)) +
  geom_point(stat="identity") +
  coord_flip() +
  theme_bw()
```

\pagebreak

#### Correlated terms
```{r Term-Associations, echo=FALSE, results='asis', fig.align='center', cache=TRUE}
assocs<-as.data.frame(findAssocs(dtm, 'globalis', 0.75))
assocs<-data.frame(row.names(assocs), assocs$globalis)
names(assocs)<-c("Terms","Globalis")
pander(assocs)
```

# Cluster analysis
```{r Cluster-Analysis, cache=TRUE}
rowtotals <- apply(dtm, 1, sum) # find the sum of words in each document
standarddtm <- dtm/rowtotals  # Thanks to Brandon Stewart for this and the code below here http://faculty.washington.edu/jwilker/tft/Stewart.LabHandout.pdf
set.seed(666) # very satanic
kclusters <- kmeans(standarddtm, centers=9)
for (i in 1:length(kclusters$withinss)) {       
#For each cluster, this defines the documents in that cluster
    inGroup <- which(kclusters$cluster==i)
    within <- standarddtm[inGroup,]
    if(length(inGroup)==1) within <- t(as.matrix(within))
    out <- standarddtm[-inGroup,]
    words <- apply(within,2,mean) - apply(out,2,mean) #Take the difference in means for each term
    print(c("Cluster", i), quote=F)
    labels <- order(words, decreasing=T)[1:20] #Take the top 20 Labels
    print(names(words)[labels], quote=F) #From here down just labels
    if(i==length(kclusters$withinss)) {
      print("Cluster Membership")
      print(table(kclusters$cluster))
      print("Within cluster sum of squares by cluster")
      print(kclusters$withinss)
    }
}
```

# Appendix

This is the appendix.

```{r Document-Lengths, echo=FALSE, cache=TRUE, fig.cap="Document lengths"}
hist<-as.data.frame(apply(dtm, 1, sum))
ggplot(hist, aes(x=hist[,1])) + geom_histogram() + theme_bw() + labs(title="Distribution of document lengths", x="Number of terms in document", y="Count of documents")
```

```{r Cluster-Diagnostics, echo=FALSE, cache=TRUE, fig.cap="Binwidth"}
summary(kclusters)
set.seed(666)
wss <- (nrow(standarddtm)-1)*sum(apply(standarddtm,2,var))
for (i in 2:10) wss[i] <- sum(kmeans(standarddtm,
                                     centers=i)$withinss)
wss<-as.data.frame(wss)
wss$numbers<-1:10
ggplot(wss, aes(x=numbers, y=wss)) +
                      geom_line() +
                      theme_bw() +
                      labs(title="Within group sum of squares by number of clusters",
                           x="Number of clusters",
                           y="Within groups sum of squares")
```

\pagebreak

# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent